MaxEnt: What is it good for?

### 2015-06-16 ms.tex
Mention I
More writing

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $\{A_1, A_2, ..., A_N\}$. One and only one of these
propositions is true, but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_6$) is $p_5/(p_5 + p_6)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

@@

\section{A special case: expected values}\label{sec:expectations}
Refer to Jaynes here...I don't want to present all the details.

>>>>

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will sometimes
describe as possible values $\{x_1, x_2, ..., x_N\}$ of an unknown variable $x$.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true, but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_6$) is $p_5/(p_5 + p_6)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

@@

\section{A special case: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

\begin{eqnarray}
\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
\end{eqnarray}

The resulting posterior distribution given by MaxEnt is:

\begin{eqnarray}
p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
\end{eqnarray}
